Large-scale spatiotemporal variation in vital rates and population dynamics of an alpine bird

### 2024-07-10 Manuscript_Nater_etal.qmd
Updated figure 1

![Simplified graphical representation of the ptarmigan life cycle with two age classes and the data sources included in the integrated distance sampling model. The pink "x"'s indicate the added dimension for area. Juv\[x,t\] = juveniles in area x year t. Ad\[x,t\] = adults in area x in year t. R\[x,t\] = recruitment rate in area x in year t. S\[x,t\] = survival probability from year t to t+1 in area x. Note that the additional site (=transect) dimension, "j", is omitted for the sake of illustration.](Figures/RypeIDSM_multiArea_structure.png){#fig-model}

>>>>

![Graphical representation of the ptarmigan life cycle with two age classes and the data sources, as well as joint distributions, included in the integrated distance sampling model. Indices $t$ denote year while $x$ represent the added dimension for area (corresponding to 41 reporting districts). Juvenile~x,t~ = juveniles in area $x$ year $t$. Adult~x,t~ = adults in area $x$ in year $t$. $R_{x,t}$ = recruitment rate in area $x$ in year $t$. $S_{x,t}$ = survival probability from year $t$ to $t+1$ in area $x$. Note that the additional site (=transect) dimension, $j$, is omitted for the sake of illustration.](Figures/RypeIDSM_multiArea_structure.png){#fig-model}
